Multi-view 3D Aerosol Distribution Recovery

### 2013-07-28 article.tex
bookmark

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the }
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
the reconstructions based on the Single-Scattering images and MC
images respectively.

>>>>

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
the reconstructions based on the Single-Scattering images and MC
images respectively. We used the distribution reconstructed based on
the MC images to create images using the Single-Scattering
model. \cref{fig:simulation-results1}c shows a cross of such an image
compared to the original MC image.
